Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-13 sections/correlated-sicm-and-fm.tex
Moved Schultz2019 to SICM/confocal since it is not surface scanning

Seifert et al. \cite{Seifert2017} investigated the morphological activity of
platelets by time-lapse SICM and subsequently obtained confocal recordings of
cytoskeletal proteins of the investigated cells, allowing them to correlate
the activity of the platelets and the structure of the cytoskeleton.

@@

SSCM has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014} and for investigating the
differentiation of stem cells \cite{Gorelik2008}. The SSCM has also been used for correlating 
topography and t-tubule distribution in cardiomyocytes \cite{Lyon2012} or for investigating 
intracellular contacts by correlating topography with the distribution of connexin-43 (Cx43) 
\cite{Schultz2019}. Furthermore, it has been utilized in studies investigating endocytotic 
pathways \cite{Shevchuk2008} (Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative 
closing mechanism for clathrin-coated pits by recording topography simultaneously with
the fluorescence of tagged actin-binding protein and the tagged
clathrin light-chain \cite{Shevchuk2012}. A further study on clathrin-mediated endocytosis revealed the effect of mutations in the Dynamin~2
gene on the maturation and internalisation of clathrin coated pits \cite{Ali2019}.

>>>>

Seifert et al. \cite{Seifert2017} investigated the morphological activity of
platelets by time-lapse SICM and subsequently obtained confocal recordings of
cytoskeletal proteins of the investigated cells, allowing them to correlate
the activity of the platelets and the structure of the cytoskeleton.
In co-cultures of cardio-myocytes and myofibroblasts, the dynamics of
myocyte-myofibroblast connection was linked to the expression of connexin-43
\cite{Schultz2019}.

@@

SSCM has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014}, for investigating
the differentiation of stem cells \cite{Gorelik2008} and the correlation of
topography and T-tubule distribution in cardiomyocytes \cite{Lyon2012} during
recovery from heart failure. Furthermore, it has been utilized in studies
investigating endocytotic pathways \cite{Shevchuk2008}
(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
mechanism for clathrin-coated pits by recording topography simultaneously with
the fluorescence of tagged actin-binding protein and the tagged clathrin
light-chain \cite{Shevchuk2012}. A further study on clathrin-mediated
endocytosis revealed the effect of mutations in the Dynamin~2 gene on the
maturation and internalisation of clathrin coated pits \cite{Ali2019}.
